Stochastic Blockmodels for Relational Event Data

### 2012-05-24 docs/submission.tex
Small changes to slides and tex draft.
Work in Model section in draft.

%Each interaction then has a set of periods $d \in D_{ij}$ each with a start time $a_d$, an end time $b_d$, and a rate $\lambda_d$.
Consider a nonhomogeneous Poisson process with  intensity $\lambda(t)$ that is piecewise constant with respect to a set of knots $\tau$.  We can then write the likelihood of $M$ events as
\begin{align}
\mathcal{L}(\mathcal{A}|\theta) &= \prod_{m=1}^M \lambda(t_m) \exp\left\{ - \int_{0}^{t_M} \lambda(s)ds \right\} \\
&= \prod_{m=1}^M \lambda(t_m) \prod_{k=1}^{|\tau|} \exp\left\{ - (\tau_{k} - \tau_{k-1}) \lambda(\tau_k) \right\}
\end{align}
\noindent where the $m$th event occurs at time $t_m$, the intensity function $\lambda(t)$ is left continuous, and each $\tau_k \in [0,t_M]$.
% \begin{align}
% \mathcal{L}(A|\theta) &= \prod_{m=1}^M \lambda_{i_m}(t_m|\cdot) \prod_{i \in \mathcal{R}}  \exp\left\{ - \int_{0}^{t_M} \lambda_{i}(\tau | \cdot)d\tau \right\} \\
% &= \prod_{m=1}^M \lambda_{i_m}(t_m|\cdot) \prod_{i \in \mathcal{R}} \prod_{v \in D_{i}} \exp\left\{ - (b_v - a_v) \lambda_{i}(b_v | \cdot ) \right\}
% \end{align}

One can extend the above to marked point processes where each event contains additional information.  In the context of relational events occurring among $N$ nodes, each event in the process contains both a sender $i$ and a recipient $j$ such that  $(i,j) \in \mathcal{R}$, where $\mathcal{R}$ is the \emph{risk set} comprised of all allowed dyads.  We assume each dyad $(i,j) \in \mathcal{R}$ occurs as a Poisson process with intensity $\lambda_{ij}(t)$ that is piecewise constant.  We can then write the likelihood as  
\begin{align}
\mathcal{L}(\mathcal{A}|\theta) &= \prod_{m=1}^M \lambda_{i_m,j_m}(t_m|\cdot) \prod_{(i,j) \in \mathcal{R}_{i_m,j_m}}\exp\{ - (t_m - \tau_{mij}) \lambda_{ij}(t_m | z_i,z_j) \}
\label{eqn:llk}
\end{align}
\noindent where event $m$ is the dyad $(i_m,j_m)$, $\tau_{mij}$ is the time  of the changepoint for $\lambda_{i,j}$ prior to the $m$th event, and $\mathcal{R}_{i,j}$ is the set of dyads whose intensity changes if $(i,j)$ occurs  \cite{Butts2008}. \footnote{We further assume 1) all intensity functions change at times $t=0$ and $t=t_M$, and 2) the first event is drawn uniformly from the risk set.}

\begin{figure}

\centering 
\subfigure[Dynamic network data]
{
\begin{tikzpicture}[scale=.8,transform shape,thick]
  \node[vertex] (n1) at (0,0)  {1};
  \node[vertex] (n2) at (2,2)  {2};
  \node[vertex] (n3) at (4,0) {3};
  \node[vertex] (n4) at (2,-2) {4};
\draw[-stealth] (.4,.4) -- (1.6,1.6);
\draw[-stealth] (2.4,1.6) -- (3.6,.4);
\node at (.7,1.1) {$t_1$};
\node at (3.3,1.1) {$t_2$};
\end{tikzpicture}
}
\subfigure[Intensities for two dyads]
{
\begin{tikzpicture}[scale=1,transform shape,thick]
\draw[-stealth] (0,0) -- (0,3);
\draw[-stealth] (0,0) -- (5,0);

@@

For a given dyad $(i,j)$ and time $t$ we may also have a vector of statistics $\mathbf{s}(t,i,j|\mathcal{A}_t,\mathbf{z})$ that is a function of the previous event history  $\mathcal{A}_t = \{(t_m,i_m,j_m): t_m \in [0,t)\}$.   In practice we may believe an interaction between one dyad should not affect the rate of an entirely separate dyad.  As shown in Figure \ref{fig:example}, we incorporate this idea by assuming each intensity function $\lambda_{ij}(t)$ can only change following an event involving either $i$ or $j$.  This implies that  $\mathcal{R}_{i,j}$ is the set of dyads involving either $i$ or $j$ and that we will only use  statistics $\mathbf{s}(t,i,j)$ that do not change until an event involving either $i$ or $j$ occurs.

We hope to learn about the dynamics between subsets of nodes.   To facilitate this, we assume each node $i$ is assigned a latent cluster $z_i$ and use a log linear model for the intensity functions
\begin{align*}
\log \lambda_{ij}(t | \mathcal{A}_t,\mathbf{z}) &= \boldsymbol{\beta}_{z_i,z_j} \mathbf{s}(t,i,j|\mathcal{A}_t) &
z_i &\sim \mbox{CRP}(\alpha) &
\boldsymbol{\beta}_{k,l} &\sim \mbox{N}_p(\boldsymbol{\mu},\boldsymbol{\sigma}^2I)
\end{align*}
where for each pair of clusters $(z_i,z_j)$ we have a vector of parameters $\boldsymbol{\beta}_{z_i,z_j}$ that corresponds to the vector of statistics $\mathbf{s}(t,i,j|\cdot)$.   Thus, the model of dynamics for the dyad $(i,j)$ has the same parameters as for other dyads occurring between group $z_i$ and $z_j$.  We allow  the blocks to share information by placing a hierarchical prior on the collection of $\boldsymbol{\beta}_{k.l}$ where $\mu_p \sim N(0,1)$ and $\sigma_p \sim \mbox{Gamma}(3,1)$ (TODO).

@@

In Table \ref{tab:stats} we list the statistics we use in our experiments for  $\mathbf{s}(t,i,j)$.  Several statistics use $v_{mij} \in [0,M]$, the index of the last event where $(i,j)$ occurred (n.b. $t_{v_{mij}} = \tau_{mij}$). If $(i,j)$ has never occurred, we set $v_{mij}=0$.  We include degree effects to model possible rich-get-richer phenomenon.  For example, a particular node sending often may indicate they will continue to be a sender in the future.  We normalize these counts by the number of events up until a dyad's prior changepoint.\footnote{This seems to avoid ``explosion'' when simulating from the model.  TODO: Explore the theory about these sorts of statistics.  Aalen has a few suggestions.} Other statistics could be of interest for particular substantive questions \cite{Butts2008,Vu2011}.  \footnote{Describe the form of $f()$.  Right now it is $f(x) = \log \frac{x+1}{m + N(N-1)}$.}

@@

We use Gibbs sampling to sample the latent class assignments $\mathbf{z}$ from the conditional distribution
\begin{align*}
p(z_i | \mathbf{z}_{-i},\mathcal{A},\alpha,\boldsymbol{\beta}) &\propto p(z_i | \mathbf{z}_{-i},\alpha) p(\mathcal{A}|\mathbf{z},\boldsymbol{\beta},\mbox{node} \ i \ \mbox{involved}) \\
p(\mathcal{A}|\mathbf{z},\boldsymbol{\beta},\mbox{node} \ r \ \mbox{involved}) &= \prod_{a \in \mathcal{U}_r} \lambda_{i_a,j_a}(t_a|\cdot)
\prod_{(i,j) \in \mathcal{R}_{i_a,j_a}} \exp \{ -(t_a - \tau_{aij}) \lambda_{ij}(t_a|\cdot)\}
\end{align*}
where $\mathcal{U}_r = \{a: r \in \{i_a,j_a\}, a \in [1,M]\}$ is the set of events where node $r$ is involved.  Under a CRP($\alpha$) prior, we have $p(z_i = k | z_{-i},\alpha) = n_k $ and $p(z_i = \mbox{new} |  z_{-i},\alpha) = \alpha$ where $n_k$ is the number of nodes assigned to cluster $k$. 
% \begin{align*}
% p(z_i = k | z_{-i},\alpha) &= n_k & p(z_i = \mbox{new} |  z_{-i},\alpha) &= \alpha
% \end{align*}

 By limiting the changepoints to times when either node is involved, computing the likelihood $p(A|z,\beta,\mbox{node} \ r \ \mbox{involved})$ is $O(|\mathcal{U}_r| \cdot P \cdot N)$.  We precompute $\tau_{m,i,j}$ and $\mathbf{s}(t_m,i,j)$ for all $m,i,j$.

@@

For each block $(k,l)$ we need to sample the vector of parameters $\boldsymbol{\beta}_{k,l}$ from its posterior
\begin{align*}
p(\boldsymbol{\beta}_{k,l} | \mathcal{A}_t, \textbf{z}, \boldsymbol{\mu}, \boldsymbol{\sigma}) &\propto p(\boldsymbol{\beta}_{k,l} | \boldsymbol{\mu}, \boldsymbol{\sigma}) p( \mathcal{A}| \textbf{z}, \boldsymbol{\beta}, \mbox{cluster} \ k \ \mbox{or} \ l \ \mbox{involved}) \\  
p(\boldsymbol{\beta}_{k,l} | \mu, \sigma) &= \prod_{p=1}^Pp(\beta_{k,l,p}|\mu_p,\sigma_p^2)\\
p(\mathcal{A}|\mathbf{z},\boldsymbol{\beta}, \mbox{cluster} \ k \ \mbox{or} \ l \ \mbox{involved}) &= \prod_{a \in \mathcal{U}_r} \lambda_{i_a,j_a}(t_a|\cdot)
\prod_{(i,j) \in \mathcal{R}_{i_a,j_a}} \exp \{ -(t_a - \tau_{aij}) \lambda_{ij}(t_a|\cdot)\}
\end{align*}
where $\mathcal{V}_{k,l} = \{a: z_{i_a} \in \{k,l\} \ \mbox{or} \ z_{j_a} \in \{k,l\}, a \in [1,M]\}$ is the set of events $a$ where one of the nodes is either in block $k$ or $l$.  \footnote{TODO: If we end up using HMC, mention step size and step length used.}
This distribution is sampled using slice sampling.\footnote{We may also use HMC for this.}

@@

Though the dyad counts for the synthetic data set suggest a stochastic blockmodel (as seen in Figure  \ref{fig:syncounts}),  the center plot shows each block has empirical differences in their dynamics.  Intensities for reciprocal actions among nodes in block 1 are $e^3$ times greater, intensities for turn-taking actions among nodes in group 2 are $e^2$ times greater, and intensities for dyadic interactions between the two groups have a multiplicative effect of $e^{-1}$ and thus occur less often.  Fitting the model with $K=2$ makes the same predictions as the true model (see Table \ref{tab:results}) and the posterior credible intervals of the parameters cover the true parameter values (see Figure \ref{fig:syncounts}c).

@@

@@

 The Metropolis-Hastings acceptance probabilities require us to compute 
$$\alpha^* =\frac{p(Y|\boldsymbol{\phi}^{s},\mathbf{z}^{s})}{p(Y|\boldsymbol{\phi}^{m},\mathbf{z}^{m})}  \frac{p(\boldsymbol{\phi}^{s})}{p(\boldsymbol{\phi}^{m})} \frac{p(\mathbf{z}^{s})}{p(\mathbf{z}^{m})} \frac{q(\mathbf{z}^{s} \rightarrow \mathbf{z}^{m})}{q( \mathbf{z}^{m} \rightarrow \mathbf{z}^{s})} \frac{q(\boldsymbol{\phi}^{s} \rightarrow \boldsymbol{\phi}^{m})}{q(\boldsymbol{\phi}^{m} \rightarrow \boldsymbol{\phi}^{s})}$$

>>>>

%Each interaction then has a set of periods $d \in D_{ij}$ each with a start time $a_d$, an end time $b_d$, and a rate $\lambda_d$.
%Consider a nonhomogeneous Poisson process with  intensity $\lambda(t)$ that is piecewise constant with respect to a set of knots $\tau$.  We can then write the likelihood of $M$ events $\mathcal{A} = (t_1, \ldots, t_M)$ with $t_m > 0$ as
Consider a sequence of events $\mathcal{A} = (0,t_1, \ldots, t_M)$ arising from a nonhomogeneous Poisson process with  intensity $\lambda(t)$.  If the intensity is left continuous and piecewise constant with respect to a set of knots $\tau$ then the likelihood can be written
\begin{align}
\mathcal{L}(\mathcal{A}|\theta) &= \prod_{m=1}^M \lambda(t_m) \exp\left\{ - \int_{0}^{t_M} \lambda(s)ds \right\} \notag  \\
&= \prod_{m=1}^M \lambda(t_m) \prod_{k=1}^{|\tau|} \exp\left\{ - (\tau_{k} - \tau_{k-1}) \lambda(\tau_k) \right\}%  \exp\left\{ - (t - \tau_{M}) \lambda(t) \right\}
\end{align}
%\noindent where the $m$th event occurs at time $t_m$, the intensity function $\lambda(t)$ is left continuous, and each $\tau_k \in [0,t_M]$.

% \begin{align}
% \mathcal{L}(A|\theta) &= \prod_{m=1}^M \lambda_{i_m}(t_m|\cdot) \prod_{i \in \mathcal{R}}  \exp\left\{ - \int_{0}^{t_M} \lambda_{i}(\tau | \cdot)d\tau \right\} \\
% &= \prod_{m=1}^M \lambda_{i_m}(t_m|\cdot) \prod_{i \in \mathcal{R}} \prod_{v \in D_{i}} \exp\left\{ - (b_v - a_v) \lambda_{i}(b_v | \cdot ) \right\}
% \end{align}

One can extend the above to marked point processes where each event contains additional information.  In the context of relational events occurring among $N$ nodes, each event in the process contains both a sender $i$ and a recipient $j$ such that  $(i,j) \in \mathcal{R}$, where $\mathcal{R}$ is the \emph{risk set} comprised of all allowed dyads.  We assume each dyad $(i,j) \in \mathcal{R}$ occurs as a Poisson process with intensity $\lambda_{ij}(t|\cdot)$ that is piecewise constant and depends on the previous history of events  $\mathcal{A}_t = \{(t_m,i_m,j_m): t_m \in [0,t) \}$.  The likelihood of an observed event history $\mathcal{A}_{t_M}$ (also denoted $\mathcal{A}$ for convenience) is
\begin{align}
\mathcal{L}(\mathcal{A}|\theta) &= \prod_{m=1}^M \lambda_{i_m,j_m}(t_m|\cdot) \prod_{(i,j) \in \mathcal{R}}\exp\{ - (t_m - t_{m-1}) \lambda_{ij}(t_m | \cdot) \}
\label{eqn:llk}
\end{align}
%\prod_{(i,j) \in \mathcal{R}}\exp\{ - (t - t_{M}) \lambda_{ij}(t | \cdot) \}.

\begin{figure}
\centering 
\subfigure[Dynamic network data]
{
\begin{tikzpicture}[scale=.8,transform shape,thick]
  \node[vertex] (n1) at (0,0)  {1};
  \node[vertex] (n2) at (2,2)  {2};
  \node[vertex] (n3) at (4,0) {3};
  \node[vertex] (n4) at (2,-2) {4};
\draw[-stealth] (.4,.4) -- (1.6,1.6);
\draw[-stealth] (2.4,1.6) -- (3.6,.4);
\node at (.7,1.1) {$t_1$};
\node at (3.3,1.1) {$t_2$};
\end{tikzpicture}
}
\subfigure[Intensities for two dyads]
{
\begin{tikzpicture}[scale=1,transform shape,thick]
\draw[-stealth] (0,0) -- (0,3);
\draw[-stealth] (0,0) -- (5,0);

@@

%This implies that  $\mathcal{R}_{i,j}$ is the set of dyads involving either $i$ or $j$ and that we will only use  statistics $\mathbf{s}(t,i,j)$ that do not change until an event involving either $i$ or $j$ occurs.

We aim to learn about the dynamics between subsets of nodes.   To facilitate this, we assume each node $i$ is assigned a latent cluster $z_i$ and use a log linear model for the intensity functions
\begin{align*}
\log \lambda_{ij}(t | \mathcal{A}_t,\mathbf{\beta},\mathbf{z}) &= \boldsymbol{\beta}'_{z_i,z_j} \mathbf{s}(t,i,j,\mathcal{A}_t)
%z_i &\sim \mbox{CRP}(\alpha) &
%\boldsymbol{\beta}_{k,l} &\sim %\mbox{N}_p(\boldsymbol{\mu},\boldsymbol{\sigma}^2I)
\end{align*}
where for each pair of clusters $(k,l)$ we have a vector of parameters $\boldsymbol{\beta}_{k,l} \sim \mbox{N}_p(\boldsymbol{\mu},\boldsymbol{\sigma}^2I)$ that corresponds to the vector of $P$ statistics $\mathbf{s}(t,i,j,\mathcal{A}_t)$ computed from the previous history $\mathcal{A}_t$.  Thus, our model for the rate of $(i,j)$ events has the same parameters as for other dyads occurring between group $z_i$ and $z_j$.

 In practice we may believe an interaction between one dyad should not affect the rate of an entirely separate dyad.  As shown in Figure \ref{fig:example}, we allow each intensity function $\lambda_{ij}(t)$ to only change following an event involving either $i$ or $j$.  In the Appendix we show how this reduces the computational complexity of computing the above likelihood.\footnote{This is analogous to a Markov condition for this class of models.}

We allow the blocks to share information by placing a hierarchical prior on the collection of $\boldsymbol{\beta}_{k.l}$ where $\mu_p \sim N(0,1)$ and $\sigma_p^2 \sim \mbox{Gamma}(3,1)$ (TODO).

@@

In Table \ref{tab:stats} we list the statistics we use in our experiments for  $\mathbf{s}(t,i,j)$.  Several statistics use $v_{mij} \in [0,M]$, the index of the last event where $(i,j)$ occurred.  % (n.b. $t_{v_{mij}} = \tau_{mij}$). 
If $(i,j)$ has never occurred, we set $v_{mij}=0$.  We include degree effects to model possible rich-get-richer phenomenon.  For example, a particular node sending often may indicate they will continue to be a sender in the future.  We normalize these counts by the number of events up until a dyad's prior changepoint.\footnote{This seems to avoid ``explosion'' when simulating from the model.  TODO: Explore the theory about these sorts of statistics.  Aalen has a few suggestions.} Other statistics could be of interest for particular substantive questions \cite{Butts2008,Vu2011}.  \footnote{Describe the form of $f()$.  Right now it is $f(x) = \log \frac{x+1}{m + N(N-1)}$.}

@@

We use Gibbs sampling to sample the latent class assignments $\mathbf{z}$ from the conditional distribution
% \begin{align*}
% p(z_r | \mathbf{z}_{-r},\mathcal{A}_t,\alpha,\boldsymbol{\beta}) &\propto p(z_i | \mathbf{z}_{-i},\alpha) p(\mathcal{A}_t|\mathbf{z},\boldsymbol{\beta}) \\
% p(\mathcal{A}|\mathbf{z},\boldsymbol{\beta},\mbox{node} \ r \ \mbox{involved}) &= \prod_{m=1}^M \lambda_{i_a,j_a}(t_a|\cdot)
% \prod_{(i,j) \in \mathcal{R}_{i_a,j_a}} \exp \{ -(t_a - \tau_{aij}) \lambda_{ij}(t_a|\cdot)\}
% \end{align*}
\begin{align*}
p(z_r | \mathbf{z}_{-r},\mathcal{A},\alpha,\boldsymbol{\beta}) \propto&  p(\mathcal{A}|\mathbf{z},\boldsymbol{\beta}) p(z_r | \mathbf{z}_{-r},\alpha) \\
p(\mathcal{A}|\mathbf{z},\boldsymbol{\beta}) \propto &
\prod_{m=1}^M \lambda_{i_m,j_m}(t_m|\cdot)^{I(r \in \{i_m,j_m\})}  \prod_{(i,j) \in \mathcal{R}_r} \exp \{ -(t_m - t_{m-1}) \lambda_{ij}(t_m|\cdot)\} 
%& \prod_{(i,j) \in \mathcal{R}_r} \exp \{ -(t - t_{M}) \lambda_{ij}(t|\cdot)\}  
\end{align*} 
where $\mathcal{R}_r = \{(i,j) \in \mathcal{R}: r \in \{i,j\}\}$ is the set of dyads involving node $r$.  Under a CRP($\alpha$) prior, we have $p(z_i = k | z_{-i},\alpha) = n_k $ and $p(z_i = \mbox{new} |  z_{-i},\alpha) = \alpha$ where $n_k$ is the number of nodes assigned to cluster $k$. 
% \begin{align*}
% p(z_i = k | z_{-i},\alpha) &= n_k & p(z_i = \mbox{new} |  z_{-i},\alpha) &= \alpha
% \end{align*}

@@

For each block $(k,l)$ we need to sample the vector of parameters $\boldsymbol{\beta}_{k,l}$ from its posterior
\begin{align*}
p(\boldsymbol{\beta}_{k,l} | \mathcal{A}, \textbf{z}, \boldsymbol{\mu}, \boldsymbol{\sigma}) &\propto p(\boldsymbol{\beta}_{k,l} | \boldsymbol{\mu}, \boldsymbol{\sigma}) p( \mathcal{A}| \textbf{z}, \boldsymbol{\beta}) \\ %, \mbox{cluster} \ k \ \mbox{or} \ l \ \mbox{involved}) \\  
p(\boldsymbol{\beta}_{k,l} | \mu, \sigma) &= \prod_{p=1}^Pp(\beta_{k,l,p}|\mu_p,\sigma_p^2)\\
p(\mathcal{A}|\mathbf{z},\boldsymbol{\beta}) &\propto \prod_{m=1}^M \lambda_{i_m,j_m}(t_m|\cdot)
\prod_{(i,j) \in \mathcal{V}_{k,l}} \exp \{ -(t_m - t_{m-1}) \lambda_{ij}(t_m|\cdot)\}
%p(\mathcal{A}|\mathbf{z},\boldsymbol{\beta}, \mbox{cluster} \ k \ \mbox{or} \ l \ \mbox{involved}) &= \prod_{a \in \mathcal{U}_r} \lambda_{i_a,j_a}(t_a|\cdot)
%\prod_{(i,j) \in \mathcal{R}_{i_a,j_a}} \exp \{ -(t_a - \tau_{aij}) \lambda_{ij}(t_a|\cdot)\}
\end{align*}
where $\mathcal{V}_{k,l} = \{(i,j): z_{i} \in \{k,l\} \ \mbox{or} \ z_{j} \in \{k,l\} \}$ is the set of dyads with a sender in group $k$ and a recipient in $l$.  This distribution is sampled using slice sampling.

@@

Though the dyad counts for the synthetic data set suggest a stochastic blockmodel (as seen in Figure  \ref{fig:syncounts}),  the center plot shows each block has empirical differences in their dynamics.  Intensities for reciprocal actions among nodes in block 1 are $e^3$ times greater, intensities for turn-taking actions among nodes in group 2 are $e^2$ times greater, and intensities for dyadic interactions between the two groups have a multiplicative effect of $e^{-1}$ and thus occur less often.  Fitting the model with $K=2$ has similar  predictive accuracy as the true model (see Table \ref{tab:results}), recovers the true latent classes, and the posterior credible intervals of the parameters cover the true parameter values (see Figure \ref{fig:syncounts}c).

@@

\appendix{\textbf{Complexity}}

We take advantage of our restriction on the types of statistics $s$ to reduce the computational complexity of computing our likelihood
 Equation \ref{eqn:likelihood} as 
\begin{align*}
\mathcal{L}(\mathcal{A}_{t_M}|\theta) &= \prod_{m=1}^M \lambda_{i_m,j_m}(t_m|\cdot) \prod_{(i,j) \in \mathcal{R}_{i_m,j_m}}\exp\{ - (t_m - \tau_{mij}) \lambda_{ij}(t_m | \cdot) \}
\end{align*}
\noindent where event $m$ is the dyad $(i_m,j_m)$, $\tau_{mij}$ is the time  of the changepoint for $\lambda_{i,j}$ prior to the $m$th event, and $\mathcal{R}_{i,j}$ is the set of dyads whose intensity changes if $(i,j)$ occurs  \cite{Butts2008}. \footnote{We further assume 1) all intensity functions change at times $t=0$ and $t=t_M$, and 2) the first event is drawn uniformly from the risk set.}

 By limiting the changepoints to times when either node is involved, computing the likelihood $p(A|z,\beta,\mbox{node} \ r \ \mbox{involved})$ is $O(|\mathcal{U}_r| \cdot P \cdot N)$.  We precompute $\tau_{m,i,j}$ and $\mathbf{s}(t_m,i,j)$ for all $m$, $i$, and $j$.

@@

 The Metropolis-Hastings acceptance probabilities require the quantity
$$\alpha^* =\frac{p(Y|\boldsymbol{\phi}^{s},\mathbf{z}^{s})}{p(Y|\boldsymbol{\phi}^{m},\mathbf{z}^{m})}  \frac{p(\boldsymbol{\phi}^{s})}{p(\boldsymbol{\phi}^{m})} \frac{p(\mathbf{z}^{s})}{p(\mathbf{z}^{m})} \frac{q(\mathbf{z}^{s} \rightarrow \mathbf{z}^{m})}{q( \mathbf{z}^{m} \rightarrow \mathbf{z}^{s})} \frac{q(\boldsymbol{\phi}^{s} \rightarrow \boldsymbol{\phi}^{m})}{q(\boldsymbol{\phi}^{m} \rightarrow \boldsymbol{\phi}^{s})}$$
